\LARGE \bf Predicting Initialization Effectiveness for Trajectory Optimization

### 2014-02-12 paper.tex
revision

We propose a learning-based approach to predict the quality of a trajectory as an initialization to the optimization-based motion planning. Here, a trajectory's quality is measured by whether the optimization problem converges to a collision-free trajectory when using the given trajectory as the initial guess. In other words, the quality is defined in a qualitative manner, i.e. `good' or `bad'.
For the learning algorithm, we first design a set of trajectory features, which are relevant to a trajectory's effectiveness as an initialization. These features are both task-independent and scene-independent, and hence they are transferable among different planning tasks. We use four types of features: 1) spatial signed distance (SSD) vectors for each robot link; 2) difference between SSD vectors for the same robot link in adjacent trajectory waypoints and for adjacent robot links in the same waypoint; 3) spherical harmonics transform of SSD vectors; and 4) features measuring the non-convexity of the constrained optimization problem close to the trajectory. These features encode the obstacle distribution locally around a robot trajectory and thus are essential for predicting a trajectory's behavior under a trajectory optimization algorithm. These features are calculated for a set of randomly selected trajectories for different tasks in various benchmarks. Next, we run trajectory optimization using these trajectories as initial guesses and obtain a labeled dataset. In the dataset, each trajectory is augmented with a `good' or `bad' label according to whether the optimization converges to a collision-free trajectory or not. With this dataset as the training set, we learn a predict function for trajectory effectiveness. We evaluate the accuracy of the learned predict function by counting the ratio of correct predictions for a set of new trajectories on various benchmarks.

@@

Robotic motion planning problems can be formulated as non-convex optimization problems, i.e., minimize an objective subject to inequality and equality constraints:
\begin{align}
\label{eq:opt}
& \underset{\x}{\text{minimize}}
& & f(\x) \\
& \text{subject to}
& & g_i(\x) \leq 0, \; i = 1, 2, \dots, n_{\text{ieq}} \notag \\
&&& h_i(\x) = 0, \; i = 1, 2, \dots, n_{\text{eq}} \notag
\end{align}
where $f$, $g_i$ and $h_i$ are scalar functions. For planning problems that involve only kinematics and represent the trajectory as a sequence of $T$ waypoints, the optimization variable $\x$ is of the form of $\x = \btheta_{1:T}$, where $\btheta_t \in \mathbb{R}^K$ denotes the configuration at the $t$-th waypoint for a system with $K$ degrees of freedom. For problems with dynamics, the optimization variable $\x$ may also include velocities $\dot{\btheta_t}$ and torques ${\bm \tau}_t$.

@@

\subsection{Effectiveness Prediction on Same Benchmarks}
We first show the prediction accuracy when using a classifier learned on one benchmark to predict the effectiveness of trajectories in the same benchmark but for different tasks. The results are shown in Table~\ref{tab:result}, where we compare the baseline accuracy and the accuracy when different combinations of features are used to train a classifier. From the results, we observe that the learned classifiers provide accuracy significantly higher than the baseline (which simply predict according to the majority label in the training set). However, the peak accuracy may be achieved by different combination of features on different benchmarks.

>>>>

We propose a learning-based approach to predict the quality of a trajectory as an initialization to the optimization-based motion planning. Here, a trajectory's quality is measured by whether the optimization problem converges to a collision-free trajectory when using the given trajectory as the initial guess. In other words, the quality is defined in a qualitative manner, i.e. `good' or `bad'.
For the learning algorithm, we first design a set of trajectory features, which are relevant to a trajectory's effectiveness as an initialization. These features are both task-independent and scene-independent, and hence they are transferable among different planning tasks. We use four types of features: 1) spatial signed distance (SSD) vectors for each robot link; 2) difference between SSD vectors for the same robot link in adjacent trajectory waypoints and for adjacent robot links in the same waypoint; 3) spherical harmonics transform of SSD vectors; and 4) features measuring the non-convexity of the constrained optimization problem in the trajectory neighborhood. These features encode the obstacle distribution locally around a robot trajectory and thus are essential for predicting a trajectory's behavior under a trajectory optimization algorithm. We calcuate these features for a set of randomly selected trajectories for different tasks in various benchmarks. We then run optimization-based motion planning using these trajectories as initial guesses and obtain a labeled dataset. In the dataset, each trajectory is augmented with a `good' or `bad' label according to whether the optimization converges to a collision-free trajectory. With this dataset as the training set, we learn a predict function for trajectory effectiveness. We evaluate the accuracy of the learned predict function by counting the ratio of correct predictions for a set of new trajectories on various benchmarks.

@@

Robotic motion planning problems can be formulated as non-convex optimization problems, i.e., minimize an objective subject to inequality and equality constraints:
\begin{align}
\label{eq:opt}
& \underset{\x}{\text{minimize}}
& & f(\x) \\
& \text{subject to}
& & g_i(\x) \leq 0, \; i = 1, 2, \dots, n_{\text{ieq}} \notag \\
&&& h_i(\x) = 0, \; i = 1, 2, \dots, n_{\text{eq}} \notag
\end{align}
where $f$, $g_i$ and $h_i$ are scalar functions. For planning problems that involve only kinematics and represent the trajectory as a sequence of $T$ waypoints, the optimization variable $\x$ is of the form $\x = \btheta_{1:T}$, where $\btheta_t \in \mathbb{R}^K$ denotes the configuration at the $t$-th waypoint for a system with $K$ degrees of freedom. For problems with dynamics, the optimization variable $\x$ may also include velocities $\dot{\btheta_t}$ and torques ${\bm \tau}_t$.

@@

\subsection{Effectiveness Prediction on Same Benchmarks}
We first show the prediction accuracy when using a classifier learned on one benchmark to predict the effectiveness of trajectories in the same benchmark but for different tasks. The results are shown in Table~\ref{tab:result}, where we compare the baseline accuracy and the accuracy when different combinations of features are used to train a classifier. From the results, we observe that the learned classifiers provide accuracy significantly higher than the baseline (which simply predicts according to the majority label in the training set). However, the peak accuracy may be achieved by different combination of features on different benchmarks.
